Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-19 docs/thesis/chap-evaluation.tex
added 5th equation

Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
 } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline

>>>>

Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math><msub><mi>G</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>=</mo><msub><mi>R</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>-</mo><mfrac><mn>1</mn><mn>2</mn></mfrac><mi>R</mi><msub><mi>g</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>=</mo><mfrac><mrow><mn>8</mn><mi>π</mi><mi>G</mi></mrow><msup><mi>c</mi><mn>4</mn></msup></mfrac><msub><mi>T</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub></math>
 </math>
 } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
